---
title: "HW5"
author: "Alison Wyatt and Kylie Knudten"
date: "`r Sys.Date()`" 
output: pdf_document
---

```{r}
library(ggplot2)
choco <- read.csv("https://ds202-at-isu.github.io/labs/data/choco.csv")
head(choco)
```
# Question Set 1

1. What is the overall number of chocolate bars rated?

```{r}
str(choco)
mean(choco$Rating)
```
There are a total of 1,852 chocolate bars rated, with an average rating of 3.19. 

2. How does the number of ratings depend on the year? Draw a bar chart of the number of reports.

```{r}
choco$Review.Date <- factor(choco$Review.Date)
ggplot(data=choco,aes(x=Review.Date)) + geom_bar(aes(weight=Rating))
```

From 2006 to 2015, the barchart shows a steady increase in number of ratings each year. 2016 through 2017, the last couple years of testing, show a decrease.

# Question Set 2

1. How are ratings distributed? Draw a histogram of ratings and describe it. Don’t forget to mention outliers, if there are any.

```{r}
ggplot(choco,aes(x = Rating)) + geom_histogram(binwidth=0.25)
```
This distribution is bimodal, with modes around 2.75 and 3.5. It is not symmetric and has a slight skew to the right. There are potential outliers at 1, 1.5, and 5. 

2. Do ratings depend on the cocoa percentage of a chocolate bar?
```{r}
ggplot(data=choco, aes(x=Cocoa.Pct, y = Rating)) + geom_jitter()
```

There is no clear pattern in the scatterplot that indicates a relationship/correlation between cocoa percentage and rating.

3. How do ratings compare across different company locations? Focus on the three locations with the most ratings:

```{r}
<- dplyr::filter(choco, Company.Location %in% c("U.S.A.", "France", "Canada"))
```

