---
title: "HW5"
author: "Alison Wyatt and Kylie Knudten"
date: "`r Sys.Date()`" 
output: pdf_document
---
Github link: https://github.com/aawyatt/Lab-2

```{r}
library(ggplot2)
choco <- read.csv("https://ds202-at-isu.github.io/labs/data/choco.csv")
head(choco)
```
# Question Set 1

1. What is the overall number of chocolate bars rated?

```{r}
str(choco)
mean(choco$Rating)
```
There are a total of 1,852 chocolate bars rated, with an average rating of 3.19. 

2. How does the number of ratings depend on the year? Draw a bar chart of the number of reports.

```{r}
choco$Review.Date <- factor(choco$Review.Date)
ggplot(data=choco,aes(x=Review.Date)) + geom_bar(aes(weight=Rating))
```

From 2006 to 2015, the barchart shows a steady increase in number of ratings each year. 2016 through 2017, the last couple years of testing, show a decrease.

# Question Set 2

1. How are ratings distributed? Draw a histogram of ratings and describe it. Don’t forget to mention outliers, if there are any.

```{r}
ggplot(choco,aes(x = Rating)) + geom_histogram(binwidth=0.25)
```
This distribution is bimodal, with modes around 2.75 and 3.5. It is not symmetric and has a slight skew to the right. There are potential outliers at 1, 1.5, and 5. 

2. Do ratings depend on the cocoa percentage of a chocolate bar?
```{r}
ggplot(data=choco, aes(x=Cocoa.Pct, y = Rating)) + geom_jitter()
```

There is no clear pattern in the scatterplot that indicates a relationship/correlation between cocoa percentage and rating.

3. How do ratings compare across different company locations? Focus on the three locations with the most ratings:

```{r}
locations <- dplyr::filter(choco, Company.Location %in% c("U.S.A.", "France", "Canada"))
ggplot(locations, aes(x = Rating, y = Company.Location)) + geom_boxplot()
```
All three locations have a similar mean around 3.25 and the same maximum value of 4, but the US and France have the lowest ratings recorded, at 1.5. France has the smallest range between the maximum and minimum values, excluding outliers. Canada has the largest value at the 75% quartile at 3.75. 

# Individual questions 

## Kylie's question:
How do cocoa percentages compare across the 3 company locations with the most ratings?

```{r}
locations <- dplyr::filter(choco, Company.Location %in% c("U.S.A.", "France", "Canada"))
ggplot(locations, aes(x=Cocoa.Pct,y=Company.Location)) + geom_boxplot()
```

The three company locations with the most ratings, U.S.A, France, and Canada, have slightly different means. USA and Canada have a similar mean around 70%, while France's mean is around 73-74%. USA has the largest amount of outliers on either side of the quantile function, giving it the largest overall range of values. France has the largest amount of ratings within its 25th and 75th quantiles, while USA and Canada stay fairly similar.

## Alison's question: 
Is there a relationship between REF and cocoa pct.?

```{r}
ggplot(data=choco, aes(x=Cocoa.Pct, y = REF)) + geom_jitter()
```
There doesn't seem to be a relationship between REF and cocoa percentage. The lowest cocoa percentage is around 40% and has an REF value of around 1100. The highest cocoa value, of 100%, has REF values that range from around 100 to 1750. There is no linear relationship, positive or negative. 

# Workflow reflection
The workflow was really good for this homework. We divided up the questions and were each able to work on the same R markdown file to complete our own sections. After we did each part, we committed our changes, pulled our partners changes, and then pushed our personal changes. We were able to get it done quickly as we were working on the same document. We also didn't need to have a lot of outside communication because we had divided the problems and could see each others work. 
